### 2021-04-17 paper/ase21/eval.tex
[ASE21] More eval.tex

Figure~\ref{fig:stat} shows four statistics of type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iteration, and (d)
the analysis time.  For each version of ECMAScript, \inred{1,999.9} functions
(\textsf{func}) are analyzed and \inred{1,999.9} functions among them are fully
compiled (\textsf{full-func}) on average.  Since the compile rules in $\jiset$
is more suitable for recent versions, the number of fully compiled functions in
older versions are less than in more recent versions.  $\tool$ keeps different
abstract environments for each functions divided by flow- and type-sensitive
views.  In the analysis result, \inred{1.3}M views existed for each version and
\inred{1.3}K views existed for each function on average.

We measured performance of $\tool$ based on the number of iteration for worklist
algorithm and the analysis time.  For each version of ECMAScript, $\tool$ took
\inred{300.0} seconds with \inred{19,999.9} iterations of worklist algorithm on
average.  The analysis time consists of \inred{10.0} seconds for the
specification extraction (\textsf{extract}), \inred{340.0} seconds for the type
analysis (\textsf{analyze}), \inred{10.0} seconds for the bug detection
(\textsf{detect}).

>>>>

Figure~\ref{fig:stat} shows four statistics of type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iterations, and
(d) the analysis time.  For each version of ECMAScript, \inred{1,999.9}
functions (\textsf{func}) are analyzed and \inred{1,999.9} functions among them
are fully compiled (\textsf{full-func}) on average.  Since the compile rules in
$\jiset$ is more suitable for recent versions, the number of fully compiled
functions in older versions are less than in more recent versions.  $\tool$
keeps different abstract environments for each functions divided by flow- and
type-sensitive views.  In the analysis result, \inred{1.3}M views existed for
each version and \inred{1.3}K views existed for each function on average.

We measured performance of $\tool$ based on the number of iterations for
worklist algorithm and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{300.0} seconds with \inred{19,999.9} iterations of worklist
algorithm on average.  The analysis time consists of \inred{10.0} seconds for
the specification extraction (\textsf{extract}), \inred{340.0} seconds for the
type analysis (\textsf{analyze}), \inred{10.0} seconds for the bug detection
(\textsf{detect}).
